\section{Requirements}\label{sec:requirements}
\subsection{DNS}\label{subsec:minimal-requirements-dns}
\begin{frame}{DNS}
	\setbeamercovered{dynamic} %Makes the text appear before it presents nice!!!!
	\begin{alertblock}{Updating DNS Manually:}
		\begin{itemize}
			\item<1-| alert@1> Adding records \alert{manually}!
			\item<2-| alert@2> Updating records \alert{manually}!
			\item<3-| alert@3> Deleting records \alert{manually}!
			\item<4-| alert@4> Zero to none human interaction! \alert{Automation}!
		\end{itemize}	
	\end{alertblock}
	\begin{exampleblock}{Problems that will be introduced:}
		\begin{itemize}
			\item<1-| alert@1> We are dependent on employee(s). \alert{Delay}!
			\item<2-| alert@2> What if a record in production is \alert{miss configured}?
			\item<3-| alert@3> \alert{Danger!!!} Accidentally removed record(s)!
			\item<4-| alert@4> \alert{Many different vendors}! Accommodate all?
		\end{itemize}	
	\end{exampleblock}
\end{frame}

\subsection{SSL Certificates}\label{subsec:minimal-requirements-ssl-certificates}
\begin{frame}{SSL Certificates}
	\setbeamercovered{dynamic} %Makes the text appear before it presents nice!!!!
	\begin{alertblock}{Updating SSL Certificates Manually:}
		\begin{itemize}
			\item<1-| alert@1> Creating Certificate \alert{manually}!
			\item<2-| alert@2> Updating a Certificate \alert{manually}!
			\item<3-| alert@3> Deleting a Certificate \alert{manually}!
			\item<4-| alert@4> \alert{Maximum expiration period up to two years}!
		\end{itemize}	
	\end{alertblock}
	\begin{exampleblock}{Problems that will be introduced:}
		\begin{itemize}
			\item<1-| alert@1> We are dependent on employee(s). \alert{Delay}!
			\item<2-| alert@2> Certificate is updated \alert{but not all dependencies}?
			\item<3-| alert@3> Accidentally removing a \alert{Certificate} in production!
			\item<4-| alert@4> We should be renew \alert{Certificates} more often!
		\end{itemize}	
	\end{exampleblock}
\end{frame}

\subsection{Centralized Login}\label{subsec:minimal-requirements-centralized-login}
\begin{frame}{Centralized Login}
	\setbeamercovered{dynamic} %Makes the text appear before it presents nice!!!!
	\begin{alertblock}{Login from multiple Applications:}
		\begin{itemize}
			\item<1-| alert@1> Multiple applications created by \alert{different} teams!
			\item<2-| alert@2> Multiple log \alert{levels} per application!
			\item<3-| alert@3> Logs from \alert{multiple} k8s clusters?
			\item<4-| alert@4> What is the cost of these tools on the cloud?
		\end{itemize}	
	\end{alertblock}
	\begin{exampleblock}{Problems that will be introduced:}
		\begin{itemize}
			\item<1-| alert@1> We need to use \alert{centralized solutions}!
			\item<2-| alert@2> Logs Persisten Volumes (PV) will be \alert{overloaded}!
			\item<3-| alert@3> How many tools can \alert{provide} this service?
			\item<4-| alert@4> \alert{Storage and logs} on the cloud are expensive!
		\end{itemize}	
	\end{exampleblock}
\end{frame}

\subsection{Monitoring and Visualizing}\label{subsec:minimal-requirements-monitoring}
\begin{frame}{Monitoring and Visualizing}
	\setbeamercovered{dynamic} %Makes the text appear before it presents nice!!!!
	\begin{alertblock}{Exporting metrics:}
		\begin{itemize}
			\item<1-| alert@1> More applications \alert{higher the complexity}!
			\item<2-| alert@2> \alert{Health Check} of the applications and the nodes!
			\item<3-| alert@3> Exporting \alert{network metrics} is so so important!
			\item<4-| alert@4> \alert{Visualize the Data} in the simplest format!
		\end{itemize}	
	\end{alertblock}
	\begin{exampleblock}{Problems if we do not process the Data:}
		\begin{itemize}
			\item<1-| alert@1> \alert{Metrics} per application(s) with \alert{no configurations}! 
			\item<2-| alert@2> Status (\alert{node(s) / application(s)}) is a \alert{24/7 necessity}!
			\item<3-| alert@3> \alert{Monitoring routing}! Result to observe \alert{bottlenecks}!
			\item<4-| alert@4> Data or problems should be easy to \alert{visualize}!
		\end{itemize}	
	\end{exampleblock}
\end{frame}